---
title: "311 Data Exploration"
author: "Myeong Lee"
date: "2/10/2019"
output: html_document
---


```{r, echo=FALSE}
library(maps)
library(geosphere)
library(readr)
library(dplyr)
library(magrittr)
library(lubridate)
library(rgdal)
library(raster)
library(rgeos)
require(ggplot2)
library(cwhmisc)
library(utils)
library(rpart)
library(stringr)
library(hydroGOF)
library(fields)
library(MASS)
library(tidyr)
library(raster)
library(reshape2)
library(igraph)
library(Hmisc)
library(randomForest)
library(caret)
library(leaflet)
library(RColorBrewer)
library(classInt)
library(maptools)
library(ggmap)

register_google(key="AIzaSyD36Jq79omYvK4q160enCpKcdzeuhlCu7U")
```

# Random Baseline
```{r, echo=FALSE, fig.width=10,fig.height=11}
setwd("~/git/311/")

cases = read_delim("dataverse_files/311_open.csv", delim = ",",col_names = TRUE )

# Just for testing...
# sids <- sample(cases$case_enquiry_id, 1000)
# cases <- cases[cases$case_enquiry_id %in% sids,]
cases$neighborhood <- as.factor(cases$neighborhood) #22 neighborhoods
cases$type <- as.factor(cases$type) #123 types
cases$reason <- as.factor(cases$reason) #28 reasons
cases$source <- as.factor(cases$source) #6 sources
cases$department <- as.factor(cases$department) #8 departments
cases$subject <- as.factor(cases$subject) #6 subjects

neighborhood <- readOGR("Bos_neighborhoods/Bos_neighborhoods.shp", layer="Bos_neighborhoods") %>%
  spTransform(CRS("+proj=longlat +datum=WGS84"))

idList <- neighborhood@data$OBJECTID
centroids.df <- as.data.frame(coordinates(neighborhood))
names(centroids.df) <- c("Longitude", "Latitude")  
nameList <- neighborhood@data$Name
neighbor.df <- data.frame(id = idList, name = nameList, centroids.df)

# Aggregating neighborhood names based on overlaps
cases[cases$neighborhood %in% "Allston",]$neighborhood <- "Allston / Brighton"
cases[cases$neighborhood %in% "Brighton",]$neighborhood <- "Allston / Brighton"
cases$neighborhood <- as.character(cases$neighborhood)
cases$neighborhood <- as.factor(cases$neighborhood)

map <- ggmap::get_map(location=c(-71.09, 42.305), zoom = 12, color = "bw")
# map <- ggmap::get_map(location=c(-71.09, 42.34), zoom = 13, color = "bw")
mapPoints <- ggmap(map) + 
  geom_polygon(aes(x=long, y=lat, group=group), data = neighborhood, color='red', alpha=0.4) +
  geom_point(aes(x = longitude, y = latitude, colour=neighborhood), data = cases, alpha=0.5, size=1) +
  geom_text(data=neighbor.df, aes(label = name, x = Longitude, y = Latitude)) +
  ggtitle("311 Cases") +
  theme(legend.position="bottom")
ggsave(paste0("output/", "311_cases.pdf"), mapPoints, width=9, height=9)

```


# 1. Types of 311 inquiries
```{r, fig.width=10,fig.height=11}

reasons <- cases %>% group_by(reason) %>% summarise(count=n())
reasons <- reasons[order(-reasons$count),]
ggplot(data=reasons, aes(x= reorder(reason,count),count)) +geom_bar(stat="identity") + 
  xlab("Categories (high-level)") + ggtitle("Categories of 311 Inquiries") + coord_flip()


types <- cases %>% group_by(type) %>% summarise(count=n())
types <- types[order(-types$count),]
ggplot(data=types[1:30,], aes(x= reorder(type,count),count)) +geom_bar(stat="identity") + 
  xlab("Types (specific types of problems)") + ggtitle("Specific Types of 311 Inquiries (top-30)") + coord_flip()

# All types
print(types$type)

subjects <- cases %>% group_by(subject) %>% summarise(count=n())
subjects <- subjects[order(-subjects$count),]
ggplot(data=subjects, aes(x= reorder(subject,count),count)) +geom_bar(stat="identity") + 
  xlab("Subjects (Subjects of problems)") + ggtitle("Departments that were assigned cases") + coord_flip()

sources <- cases %>% group_by(source) %>% summarise(count=n())
sources <- sources[order(-sources$count),]
ggplot(data=sources, aes(x= reorder(source,count),count)) +geom_bar(stat="identity") + 
  xlab("Reporting Mechanisms") + ggtitle("311 Reporting Source") + coord_flip()

```

### 1-1. Examples of Inquiries and Reasons for Closure (random 30 samples)
```{r}
sample_ids <- sample(cases$case_enquiry_id, 30)

for (i in sample_ids){
  text <- paste0 (cases[cases$case_enquiry_id==i,]$case_title, ": ", cases[cases$case_enquiry_id==i,]$closure_reason)
  print(text)
}

```

# 2. Inquiries across Different Neighborhoods
```{r, fig.width=10,fig.height=11}
neigh <- cases %>% group_by(neighborhood, reason) %>% summarise(count=n())
neigh <- neigh[order(-neigh$count),]
colorCount <- length(levels(neigh$reason))
getPalette = colorRampPalette(brewer.pal(12, "Paired"))

ggplot(data=neigh, aes(x= reorder(neighborhood,count), count, fill=reason)) +geom_bar(stat="identity", color="black")+
  xlab("Number of cases by reason") + ggtitle("Inquiry Reason by Neighborhood") + coord_flip() +  
  theme(legend.position="bottom") + scale_fill_manual(values = getPalette(colorCount))
```

### 2-1. Most wide-spread reasons and types of problems by neighborhood
```{r}
most <- neigh %>% group_by(neighborhood) %>% summarise (max = max(count), reason=first(reason))
colnames(most) <- c("Neighborhood", "max", "Most Siginificant Reason")

for (i in 1:nrow(most)){
  print(paste0 (most[i,]$Neighborhood, ": ", most[i,]$`Most Siginificant Reason`))
}

```


# 3. Numbers and types of individuals
This statistics cannot be analyzed because there's no data about individuals available in the public dataset (this is possible from restricted 311 datasets).

# 4. Relationships between 311 Inquiries and Socio-Economic Status
```{r, echo=FALSE, fig.width=10,fig.height=11}
socioeconomic <- readOGR("Climate_Ready_Boston_Social_Vulnerability/Climate_Ready_Boston_Social_Vulnerability.shp",
                        layer="Climate_Ready_Boston_Social_Vulnerability") %>%
  spTransform(CRS("+proj=longlat +datum=WGS84"))
socioeconomic@data$Low_to_No <- as.numeric(socioeconomic@data$Low_to_No)
socioeconomic@data$POP100_RE <- as.numeric(socioeconomic@data$POP100_RE)
socioeconomic@data$norm_low <- socioeconomic@data$Low_to_No / socioeconomic@data$POP100_RE


lnd <- SpatialPolygonsDataFrame(Sr = spTransform(socioeconomic, CRSobj = CRS("+init=epsg:4326")), 
                                data = socioeconomic@data)
lnd.f <- fortify(lnd)
lnd$id <- row.names(lnd)
lnd.f <- left_join(lnd.f, lnd@data, by=("id"))
lnd.f$norm_low <- log(lnd.f$norm_low) 

map <- ggmap::get_map(location=c(-71.09, 42.305), zoom = 12, color = "bw")
# map <- ggmap::get_map(location=c(-71.09, 42.34), zoom = 13, color = "bw")
mapPoints <- ggmap(map) + 
  geom_polygon(aes(x=long, y=lat, group=group, fill=norm_low), data = lnd.f, color='black') +
  scale_fill_continuous(low = "lightyellow", high = "red", name = "Low income density") + 
  ggtitle("Low-to-No Income Population (normalized) by Census Tract (The more red, the more low income population)") 
  # theme(legend.position="bottom")
mapPoints
```

### 4-1. Neighborhood-level Low-to-No Income Population
```{r, echo=FALSE, fig.width=10,fig.height=11}

pa1 <- aggregate(lnd, by='Name', sums=list(list(sum, 'POP100_RE'), list(sum, 'Low_to_No')))
pa1.f <- fortify(pa1)
pa1$id <- row.names(pa1)
pa1.f <- left_join(pa1.f, pa1@data, by=("id"))
pa1.f$norm_low <- log(pa1.f$Low_to_No / pa1.f$POP100_RE )

map <- ggmap::get_map(location=c(-71.09, 42.305), zoom = 12, color = "bw")
mapPoints <- ggmap(map) + 
  geom_polygon(aes(x=long, y=lat, group=group, fill=norm_low), data = pa1.f, color='black') +
  scale_fill_continuous(low = "lightyellow", high = "red", name = "Low income density") + 
  ggtitle("Low-to-No Income Population (normalized) by Neigbhorhood") 
mapPoints
```

### 4-2. How inqury types differ depending on neighborhood's poverty level?
```{r, echo=FALSE, fig.width=10,fig.height=11}
xy <- cases[,c("longitude","latitude")]
points <- SpatialPointsDataFrame(coords = xy, data = cases,
                               proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"))

agg_table <- as.data.frame(matrix(nrow=0, ncol=4))
colnames(agg_table) <- c("id", "norm_low", "reason", "count")

for (i in socioeconomic$FID){
  tryCatch({
          intersection <- raster::intersect(x = points, y = socioeconomic[socioeconomic$FID==i,])
        }, error = function(e) {
          print(paste0("Iteration ", i, ": ", e))
          return()
        })
  if (nrow(intersection@data) == 0) next
  
  norm_low <- socioeconomic[socioeconomic$FID==i,]$norm_low
  
  # Count the number of reasons of reporting per census tract
  agg <- intersection@data %>% group_by(reason) %>% summarise(count = n())
  agg$norm_low <- norm_low
  agg$id <- i
  
  agg_table <- rbind(agg_table, agg[,c("id", "norm_low", "reason", "count")])
}

ggplot(agg_table, aes(x=reorder(reason,norm_low), y=norm_low)) + geom_boxplot() + ylim(c(0,5)) + 
  geom_point() + ylab("Normalized Poverty Level (The higher, the poorer)") + coord_flip() + xlab("Inquiry Reason")

# Multivariate ANOVA
summary(aov(norm_low ~ reason, data=agg_table))
```


### 4-3. How much the number of inqury differs depending on poverty level
```{r, echo=FALSE}
norm_lows <- agg_table %>% group_by(id) %>% summarise(norm_low=max(norm_low)) 
quantiles <- summary(norm_lows$norm_low)
norm_lows$class <- ""
norm_lows[norm_lows$norm_low < quantiles[2],]$class <- "Lowest"
norm_lows[norm_lows$norm_low >= quantiles[2] & norm_lows$norm_low < quantiles[3],]$class <- "Mid-Low"
norm_lows[norm_lows$norm_low >= quantiles[3] & norm_lows$norm_low < quantiles[4],]$class <- "Mid-High"
norm_lows[norm_lows$norm_low >= quantiles[4],]$class <- "Highest"

agg_table_class <- agg_table %>% left_join(norm_lows[,c("id", "class")], by=c("id"))
agg_table_class$class <- as.factor(agg_table_class$class)
agg_table_class <- agg_table_class %>% group_by(id) %>% summarise(count = n(), class=first(class))

# Multivariate ANOVA
summary(aov(count ~ class, data=agg_table_class))

ggplot(agg_table_class, aes(x=reorder(class,count), y=count)) + geom_boxplot()  + 
  geom_point() + ylab("The number of 311 Inquiries")  + xlab("Poverty Class (4-levels)")
```

